### 2022-12-18 paper6.tex
polish references

Figure~\ref{fig:diagram} shows a schematic illustration of an example
comparative simulation study. We see that, just like non-simulation based
studies, comparative simulation studies require many decisions to be made, for
instance: How will the data be generated? How often will a simulation condition
be repeated? Which statistical methods will be compared and how are their
parameters specified? How will the performance of the methods be evaluated? The
degree of flexibility, however, is much higher for simulation studies than for
non-simulation based studies as they can often be rapidly repeated under
different conditions at practically no additional cost. This is why numerous
recommendations and best practices for design, execution and reporting of
simulation studies have been proposed \citep{Hoaglin1975, Holford2000,
  Burton2006, Smith2010, OKelly2016, Monks2018, Elofsson2019, Morris2019,
  Boulesteix2020B}. We recommend \citet{Morris2019} for an introduction to
state-of-the-art simulation study methodology.

@@

\end{tikzpicture}
}
\caption{Schematic illustration of a comparative simulation study for evaluating
  performance of methods for predicting binary outcomes, such as the example
  study in Section~\ref{sec:study}. Questionable research practices (in gray)
  can affect all aspects of the study.}
\label{fig:diagram}
\end{figure}

@@

Unfortunately, there are many questionable research practices (QRPs) which may
undermine the validity of comparative simulations studies and which can easily
go undetected under current publishing standards. Figure~\ref{fig:diagram} shows
several QRPs that may occur in the exemplary simulation study. There is often a
fine line between QRPs and legitimate research practices. For instance, a
researcher may choose to selectively report the most relevant simulation
conditions, methods and outcomes in order to streamline the results for the
reader. These practices only become questionable when they serve to confirm the
hopes and beliefs of researchers regarding a particular method. For instance, if
only conditions and outcomes are reported where the researcher's favored method
appears superior over competitor methods. Consequently, the results and
conclusions of the study will be biased in favor of this method
\citep{Niessl2021}.

@@

This article is structured as follows: We first give an illustrative list of
QRPs related to comparative simulation studies (Section \ref{sec:QRP}). With an
exemplary simulation study, we then show h?ow easy it is to present a novel,
made-up method as an improvement over others if QRPs are employed and \emph{a
  priori} simulation plans remain undisclosed (Section \ref{sec:study}). The
main inspiration for this work is drawn from similar illustrative studies which
have been conducted by \citet{Yousefi2009} and \citet{Jelizarow2010} for
benchmarking studies, and by \citet{Simmons2011} in the context of $p$-hacking
in psychological research. Recently, \citet{Niessl2021} and \citet{Ullmann2022}
expanded on QRPs in benchmarking studies with the latter also including
simulation studies. In Section~\ref{sec:recommendations}, we then provide
concrete suggestions for researchers, reviewers, editors and funding bodies to
alleviate the issues of QRPs and improve the methodological quality of
comparative simulation studies. Section~\ref{sec:discussion} closes with
limitations and concluding remarks.

\section{Questionable research practices in comparative simulation studies}
\label{sec:QRP}

There are various QRPs which threaten the validity of comparative simulation
studies (see Table~\ref{table:QRPs} for an overview). QRPs can be categorized
with respect to the stage of research at which they can occur and which other
QRPs they are related to \citep{Wicherts2016}. Typically, QRPs becomes more
problematic if they are combined with related QRPs. For example, adapting the
data-generating process to achieve a desired outcome (E2) is more problematic
when the results based on the adapted process are selectively reported (R2)
compared to reporting the results based on both the original and the adapted
process. In the following, we describe QRPs from all phases of a simulation
study, namely, design, execution and reporting.

\begin{table}[!htb]
  \caption{Types of questionable research practices (QRPs) in comparative
    simulation studies at different stages of the research process. A QRP
    becomes more problematic if combined with a related QRP, especially a
    reporting QRP.}
  \label{table:QRPs}
  \centering
  \begin{tabular}{p{.05\textwidth} p{.11\textwidth} p{.75\textwidth}}
    \toprule
    \textbf{Tag} & \textbf{Related} & \textbf{Type of QRP} \\
    \midrule
    \multicolumn{2}{p{.15\textwidth}}{\textit{Design}} & \\
    D1 & E1, R1 & Not/vaguely defining objectives of simulation study \\
    D2 & E2, R1 & Not/vaguely defining data-generating process \\
    D3 & E3, E4, R1 & Not/vaguely defining which methods will be compared and how their
                      parameters are specified \\
    D4 & E1, E5, R1 & Not/vaguely defining estimands of interest \\
    D5 & E1, E5, R1 & Not/vaguely defining evaluation criteria \\
    D6 & E6, R1 & Not/vaguely defining how to handle missing values
                  (for example, due to non-convergence of methods) \\
    D7 & E7, E8, R3 & Not justifying number of simulations \\[1em]

@@

\section{Empirical study: The Adaptive Importance Elastic Net
  (AINET)} \label{sec:study}

To illustrate the application of QRPs from Table~\ref{table:QRPs} we conducted a
simulation study. The objective of the study was to evaluate the predictive
performance of a made-up regression method termed the \emph{adaptive importance
  elastic net} (\ainet). The main idea of \ainet{} is to use variable importance
measures from a random forest for a weighted penalization of the variables in an
elastic net regression model. The hope is that this \emph{ad hoc} modification
of the elastic net model improves predictive performance in clinical prediction
modeling settings where penalized regression models are frequently used.
Superficially, \ainet{} may seem sensible, however, for the data-generating
process considered in our simulation study no advantage over the classical
elastic net is expected. For more details on the method, we refer the reader to
the simulation protocol (Appendix~\ref{appendix:protocol}). We report the
pre-registered\footnote{We use the term \emph{pre-registered} throughout to
  refer to simulation analyses conducted as pre-specified in the protocol.}
simulation study results in the online supplement. As expected, the performance
of \ainet{} was virtually identical to standard elastic net regression. \ainet{}
also did not yield any improvements over logistic regression for the
data-generating process that we considered sensible \emph{a priori} (that is,
specified based on typical conditions in clinical prediction modeling and
simulation studies from other researchers).

\begin{figure}[!htb]
  \centering
  \includegraphics[width = 0.85\textwidth]{images/paper6/ainet-results.pdf}
  \caption{Differences in Brier score with 95\% adjusted confidence intervals
    between \ainet{} and random forest (RF), logistic regression (GLM), elastic
    net (EN) and adaptive elastic net (AEN) are shown for representative
    simulation conditions (correlated covariates $\rho = 0.95$, prevalence
    $\operatorname{prev} = 0.05$, a range of sample sizes $n$ and events per
    variable (EPV), in each simulation the Brier score is computed for 10'000
    test observations; for details see Appendix~\ref{appendix:protocol}). The
    top row depicts the pre-registered results in which \ainet{} does not
    outperform any competitor uniformly, except AEN. In the second row, we apply
    QRP E2: Altering the data-generating process by adding a non-linear effect
    and sparsity. The gray arrows point from the pre-registered result to the
    results under the tweaked simulation. In the third row, QRP E3 is applied:
    EN is removed as a competitor. In the bottom row, selective reporting R2 is
    applied: Only low EPV settings are reported to give a more favorable
    impression for \ainet{}. Arrows are depicted only for non-overlapping
    confidence intervals. } \label{fig:E1}
\end{figure}

We now show how application of QRPs changes the above pre-registered
conclusions. Figure~\ref{fig:E1} illustrates different types of QRPs
sequentially applied to simulation-based evaluation of \ainet{}. The top row
depicts the pre-registered differences in Brier score (horizontal axis) between
\ainet{} and competitor methods (vertical axis) for a representative subset of
the simulation conditions. A negative difference indicates superior performance
of \ainet{}. In the second row, the arrows depict the change in the
pre-registered results after changing the data-generating process (E2). The
third row shows the result after removal of the elastic net competitor (E3).
Finally, the bottom row shows the end result where selective reporting of
simulation conditions and competitor methods (R2) is applied to give a more
favorable impression of \ainet{}. We will now discuss these QRPs in more detail.

\paragraph{Altering the data-generating process (E2)}
We could not detect a systematic performance benefit of \ainet{} over standard
logistic regression, elastic net regression, or random forest for the scenarios
specified in the protocol. For this reason, we tweaked the data-generating
process by adding different sparsity conditions and a non-linear effect. We then
found that \ainet{} outperforms logistic regression under the following
conditions: Only few variables being associated with the outcome (sparsity), a
non-linear effect and a low number of events per variable (EPV).
Figure~\ref{fig:E1} (second row) shows the changes in Brier score difference
between the pre-registered and the tweaked simulation. As can be seen, the
tweaked data-generating process leads to \ainet{} being superior to competitors
in some conditions, and at least not inferior in others.

\paragraph{Removing competitor methods (E3)}
Despite the adapted data-generating process, we still observed only minor (if
any) improvements of \ainet{} over the elastic net. In order to present \ainet{}
in a better light we could omit the comparisons with the elastic net (E3), as
shown in Figure~\ref{fig:E1} (third row). This could be justified, for example,
by arguing that for neutral comparison it is sufficient to compare a less
flexible method (logistic regression, which has no tuning parameters and
captures linear effects), a more flexible method (random forest, which has
tuning parameters and captures nonlinear relationships), and a comparably
flexible method (adaptive elastic net, which has the same tuning parameters as
AINET, but differs in the way the penalization weights are chosen).

\paragraph{Selective reporting of simulation results (R2)}
After the removal of the competitor elastic net, there are still some simulation
conditions under which \ainet{} is not superior to the remaining competitors. To
make \ainet{} appear more favorable, we thus report only simulation conditions
with low EPV, as shown in Figure~\ref{fig:E1} (fourth row). This could be
justified by the fact that journals require authors to be concise in their
reporting. Otherwise, further conditions with low EPV values could be simulated
to make the results seem more exhaustive. Focusing primarily on low EPV settings
could be justified in hindsight by framing \ainet{} as a method designed for
high-dimensional data (low sample size relative to the number of variables).

\section{Recommendations}
\label{sec:recommendations}

The previous sections painted a rather negative picture of how
undisclosed changes in simulation design, analysis and reporting
may lead to overoptimistic conclusions. In the
following, we summarize what we consider to be practical recommendations for
improving the methodological quality of simulation studies; see
Table~\ref{table:recommendations} for an overview. Our recommendations are
grouped with regards to which stakeholder they concern.

\begin{table}[!htb]
  \caption{Recommendations for improving quality of comparative simulation studies
    and preventing QRPs.}
  \label{table:recommendations}
  \centering
	\begin{tabular}{p{.95\textwidth}}
		\toprule
    \textit{Researchers} \\
    \midrule
    \vspace{-1.5em}
    \begin{itemize}
    \setlength\itemsep{0pt}
    \setlength\itemindent{-12pt}
        \item[--] Write (and possibly pre-register) simulation protocols
    \item[--] Adopt good computational practices (code review, packaging, unit-tests)
    \item[--] Share code and data (possibly in intermediate/summary form to enable
    secondary analysis)
    \item[--] Report the process of the simulation study fully and transparently
    (for instance, time-stamped protocol amendments to disclose pilot studies
    and \emph{post hoc} modifications)
    \item[--] Perform simulation analysis in a blinded manner
    \item[--] Collaborate with other research groups (possibly familiar with ``competing'' methods)
    \item[--] Disclose multiplicity and uncertainty of results (for example, with sensitivity analyses)
    \item[--] Teach simulation study methodology in statistics (post)graduate courses
    \end{itemize}

@@

\section{Conclusions} \label{sec:discussion}

@@

\section{Simulation protocol}
\label{appendix:protocol}

@@

\subsection{Aims} \label{sec:aims}

The aim of this simulation study is to systematically study the predictive
performance of \ainet{} for a binary prediction task. The simulation conditions
should resemble typical conditions found in the development of prediction models
in biomedical research. In particular we want to evaluate the performance of
\ainet{} conditional on
\begin{itemize}
  \item low- and high-dimensional covariates
  \item (un-)correlated covariates
  \item small and large sample sizes
  \item varying baseline prevalences
\end{itemize}
\ainet{} will be compared to other (penalized) binary regression models
from the literature, namely
\begin{itemize}
  \item Binary logistic regression: the simplest and most popular method for
        binary prediction
  \item Elastic net: a generalization of LASSO and ridge regression, the most
        widely used penalized regression methods
  \item Adaptive elastic net: a generalization of the most popular weighted
  penalized regression method (adaptive LASSO)
  \item Random forest: a popular, more flexible method. This method is related to
        \ainet{}, see Section~\ref{sec:methods}.
\end{itemize}
These cover a wide range of established methods with varying flexibility and
serve as a reasonable benchmark for \ainet. There are many more extensions of
the adaptive elastic net in the literature \citep[see \eg{} the review
by][]{Vidaurre2013}. However, most of these extensions focus on variable
selection and estimation instead of prediction, which is why we restrict our
focus only on the four methods above.

\subsection{Data-generating process} \label{sec:dgp}

@@

\subsection*{Test data}
In order to test the out-of-sample predictive performance, we generate a test
data set of $n_{\text{test}} = 10000$ data points in each simulation $b$.

\subsection{Estimands} \label{sec:estimands}

@@

\subsection{Methods} \label{sec:methods}

@@

\subsection{Performance measures} \label{sec:performance}

The distribution of all estimands from Section~\ref{sec:estimands} will be
assessed visually with box- and violin-plots that are stratified by method and
simulation conditions. We will also compute mean, median, standard deviation,
interquartile range, and 95\% confidence intervals for each of the estimands.
Moreover, instead of ``eye-balling'' differences in predictive performance
across methods and conditions, we will formally assess them by regressing the
estimands on the method and simulation conditions \citep[see][]{Skrondal2000}.
To do so, we will use a fully interacted model with the interaction between the
methods and the 128 simulations conditions, \ie in R notation: \texttt{estimand
  $\sim$ 0 + method:scenario}. We will rank pairwise comparison between two
methods within a single condition by their $p$-values, to more easily identify
conditions where methods show differences in predictive performance. The choice
of a significance level at which a method is deemed superior will be determined
based on preliminary simulations. We set this level to 5\%, where $p$-values
will be adjusted using the single-step method \citep{Hothorn2008} within a
single simulation condition for comparisons between \ainet{} and any other
method.

@@

\subsection{Handling exceptions} \label{sec:exceptions}

@@

Figure~\ref{fig:tiebrier} shows the differences in mean Brier score between
\ainet{} and the other methods stratified by simulation conditions. We see that
there is hardly any difference between \ainet{} and the elastic net (EN) across
all simulation conditions meaning that predictive performance of both methods
seems to be very similar in the investigated scenarios.

@@

Figure~\ref{fig:tiesbrier} shows the differences in scaled Brier score between
\ainet{} and the other methods stratified by simulation conditions. The scaled
Brier score is useful to compare the actual values of Brier scores across
conditions with different prevalence, but not so much to compare Brier scores of
different methods within a simulation condition with fixed prevalence.

We see that for most conditions the plots look like a flipped version of the
original Brier scores from Figure~\ref{fig:tiebrier}. Therefore, conclusions are
mostly the same. For very small sample sizes coupled with low prevalence and low
events per variable (the topleft plots), the scaled Brier score indicates
superiority of \ainet{} over RF and GLM, which is opposite the conclusion based
on the raw Brier score. We advise to interpret these conditions cautiously since
the prevalence prediction which is used for scaling is based on the much larger
test data set.

@@

Figure~\ref{fig:tienll} shows the differences in log-score between \ainet{} and
the other methods stratified by simulation conditions. We see that in certain
conditions, the error bars of certain methods are much larger. This is due to
the log-score's sensitivity to extreme predictions, which often happen under the
RF (and sometimes under the GLM). Despite the larger variability of the
log-score, conclusion regarding the comparison between \ainet{} and the other
methods are largely the same as under the Brier score.

@@

Figure~\ref{fig:tienll} shows the differences in area under the curve (AUC)
between \ainet{} and the other methods stratified by simulation conditions. As
with the other estimands, \ainet{} shows virtually identical performance as EN
regression across all simulation conditions. \ainet{} seems to outperform RF
across most simulation conditions, with the exception of a conditions with low
sample size ($n = 100$), medium prevalence ($\mbox{prev} = 0.05$), and low
events per variable ($\mbox{EPV} \leq 1$). GLM, typically outperforms \ainet{}
conditions with small to medium sample size ($n \leq 500$), and also in
conditions with larger sample size when the events per variable is normal to
high ($\mbox{EPV} \geq 10$) and the prevalence is small ($\mbox{prev} = 0.01$).
Finally, the AEN is worse with respect to AUC than \ainet{} across all
simulation conditions.

@@

Figure~\ref{fig:cslope} shows boxplots of calibration slopes stratified by
simulation condition and method. For each condition the percentage of
simulations where no estimate could be obtained is indicated. This usually
happened because of extreme (close to zero or one) predictions, or
non-convergence of the method itself. We caution against interpretation of the
random forest (RF) calibration slopes because this method often resulted in
predicted probabilities of zero or one, so that a calibration slope could not be
fitted.

@@

Figure~\ref{fig:clarge} shows boxplots of calibration in the large estimates
stratified by simulation condition and method. For each condition also the
percentage of simulations where no estimate could be obtained is indicated. This
usually happened because of extreme (close to zero or one) predictions.

@@

\begin{landscape}
\begin{figure}[!ht]
\center
\includegraphics[width=0.9\linewidth]{images/paper6/tie-fighter_brier_sparsity0.pdf}
\caption{Tie-fighter plot for the difference in Brier score between any method
  on the $y$-axis and \ainet{}. The 95\% confidence intervals are adjusted per
  simulation condition using the single-step method. Lower values indicate
  better performance of \ainet{}. } \label{fig:tiebrier}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}[!ht]
\center
\includegraphics[width=0.9\linewidth]{images/paper6/tie-fighter_scaledBrier_sparsity0.pdf}
\caption{Tie-fighter plot for the difference in scaled Brier score between any
  method on the $y$-axis and \ainet{}. The 95\% confidence intervals are adjusted
  per simulation condition using the single-step method. Larger
  values indicate better performance of \ainet{}. } \label{fig:tiesbrier}
\end{figure}
\end{landscape}

>>>>

Figure~\ref{fig6:diagram} shows a schematic illustration of an example
comparative simulation study. We see that, just like non-simulation based
studies, comparative simulation studies require many decisions to be made, for
instance: How will the data be generated? How often will a simulation condition
be repeated? Which statistical methods will be compared and how are their
parameters specified? How will the performance of the methods be evaluated? The
degree of flexibility, however, is much higher for simulation studies than for
non-simulation based studies as they can often be rapidly repeated under
different conditions at practically no additional cost. This is why numerous
recommendations and best practices for design, execution and reporting of
simulation studies have been proposed \citep{Hoaglin1975, Holford2000,
  Burton2006, Smith2010, OKelly2016, Monks2018, Elofsson2019, Morris2019,
  Boulesteix2020B}. We recommend \citet{Morris2019} for an introduction to
state-of-the-art simulation study methodology.

@@

\end{tikzpicture}
}
\caption{Schematic illustration of a comparative simulation study for evaluating
  performance of methods for predicting binary outcomes, such as the example
  study in Section~\ref{sec6:study}. Questionable research practices (in gray)
  can affect all aspects of the study.}
\label{fig6:diagram}
\end{figure}

@@

Unfortunately, there are many questionable research practices (QRPs) which may
undermine the validity of comparative simulations studies and which can easily
go undetected under current publishing standards. Figure~\ref{fig6:diagram} shows
several QRPs that may occur in the exemplary simulation study. There is often a
fine line between QRPs and legitimate research practices. For instance, a
researcher may choose to selectively report the most relevant simulation
conditions, methods and outcomes in order to streamline the results for the
reader. These practices only become questionable when they serve to confirm the
hopes and beliefs of researchers regarding a particular method. For instance, if
only conditions and outcomes are reported where the researcher's favored method
appears superior over competitor methods. Consequently, the results and
conclusions of the study will be biased in favor of this method
\citep{Niessl2021}.

@@

This article is structured as follows: We first give an illustrative list of
QRPs related to comparative simulation studies (Section \ref{sec6:QRP}). With an
exemplary simulation study, we then show h?ow easy it is to present a novel,
made-up method as an improvement over others if QRPs are employed and \emph{a
  priori} simulation plans remain undisclosed (Section \ref{sec6:study}). The
main inspiration for this work is drawn from similar illustrative studies which
have been conducted by \citet{Yousefi2009} and \citet{Jelizarow2010} for
benchmarking studies, and by \citet{Simmons2011} in the context of $p$-hacking
in psychological research. Recently, \citet{Niessl2021} and \citet{Ullmann2022}
expanded on QRPs in benchmarking studies with the latter also including
simulation studies. In Section~\ref{sec6:recommendations}, we then provide
concrete suggestions for researchers, reviewers, editors and funding bodies to
alleviate the issues of QRPs and improve the methodological quality of
comparative simulation studies. Section~\ref{sec6:discussion} closes with
limitations and concluding remarks.

\section{Questionable research practices in comparative simulation studies}
\label{sec6:QRP}

There are various QRPs which threaten the validity of comparative simulation
studies (see Table~\ref{table6:QRPs} for an overview). QRPs can be categorized
with respect to the stage of research at which they can occur and which other
QRPs they are related to \citep{Wicherts2016}. Typically, QRPs becomes more
problematic if they are combined with related QRPs. For example, adapting the
data-generating process to achieve a desired outcome (E2) is more problematic
when the results based on the adapted process are selectively reported (R2)
compared to reporting the results based on both the original and the adapted
process. In the following, we describe QRPs from all phases of a simulation
study, namely, design, execution and reporting.

\begin{table}[!htb]
  \caption{Types of questionable research practices (QRPs) in comparative
    simulation studies at different stages of the research process. A QRP
    becomes more problematic if combined with a related QRP, especially a
    reporting QRP.}
  \label{table6:QRPs}
  \centering
  \begin{tabular}{p{.05\textwidth} p{.11\textwidth} p{.75\textwidth}}
    \toprule
    \textbf{Tag} & \textbf{Related} & \textbf{Type of QRP} \\
    \midrule
    \multicolumn{2}{p{.15\textwidth}}{\textit{Design}} & \\
    D1 & E1, R1 & Not/vaguely defining objectives of simulation study \\
    D2 & E2, R1 & Not/vaguely defining data-generating process \\
    D3 & E3, E4, R1 & Not/vaguely defining which methods will be compared and how their
                      parameters are specified \\
    D4 & E1, E5, R1 & Not/vaguely defining estimands of interest \\
    D5 & E1, E5, R1 & Not/vaguely defining evaluation criteria \\
    D6 & E6, R1 & Not/vaguely defining how to handle missing values
                  (for example, due to non-convergence of methods) \\
    D7 & E7, E8, R3 & Not justifying number of simulations \\[1em]

@@

\section{Empirical study: The Adaptive Importance Elastic Net
  (AINET)} \label{sec6:study}

To illustrate the application of QRPs from Table~\ref{table6:QRPs} we conducted
a simulation study. The objective of the study was to evaluate the predictive
performance of a made-up regression method termed the \emph{adaptive importance
  elastic net} (\ainet). The main idea of \ainet{} is to use variable importance
measures from a random forest for a weighted penalization of the variables in an
elastic net regression model. The hope is that this \emph{ad hoc} modification
of the elastic net model improves predictive performance in clinical prediction
modeling settings where penalized regression models are frequently used.
Superficially, \ainet{} may seem sensible, however, for the data-generating
process considered in our simulation study no advantage over the classical
elastic net is expected. For more details on the method, we refer the reader to
the simulation protocol (Appendix~\ref{app6:protocol}). We report the
pre-registered simulation study results in the online supplement (we use the
term \emph{pre-registered} throughout to refer to simulation analyses conducted
as pre-specified in the protocol). As expected, the performance of \ainet{} was
virtually identical to standard elastic net regression. \ainet{} also did not
yield any improvements over logistic regression for the data-generating process
that we considered sensible \emph{a priori} (that is, specified based on typical
conditions in clinical prediction modeling and simulation studies from other
researchers).

\begin{figure}[!htb]
  \centering
  \includegraphics[width = 0.85\textwidth]{images/paper6/ainet-results.pdf}
  \caption{Differences in Brier score with 95\% adjusted confidence intervals
    between \ainet{} and random forest (RF), logistic regression (GLM), elastic
    net (EN) and adaptive elastic net (AEN) are shown for representative
    simulation conditions (correlated covariates $\rho = 0.95$, prevalence
    $\operatorname{prev} = 0.05$, a range of sample sizes $n$ and events per
    variable (EPV), in each simulation the Brier score is computed for 10'000
    test observations; for details see Appendix~\ref{app6:protocol}). The
    top row depicts the pre-registered results in which \ainet{} does not
    outperform any competitor uniformly, except AEN. In the second row, we apply
    QRP E2: Altering the data-generating process by adding a non-linear effect
    and sparsity. The gray arrows point from the pre-registered result to the
    results under the tweaked simulation. In the third row, QRP E3 is applied:
    EN is removed as a competitor. In the bottom row, selective reporting R2 is
    applied: Only low EPV settings are reported to give a more favorable
    impression for \ainet{}. Arrows are depicted only for non-overlapping
    confidence intervals. } \label{fig6:E1}
\end{figure}

We now show how application of QRPs changes the above pre-registered
conclusions. Figure~\ref{fig6:E1} illustrates different types of QRPs
sequentially applied to simulation-based evaluation of \ainet{}. The top row
depicts the pre-registered differences in Brier score (horizontal axis) between
\ainet{} and competitor methods (vertical axis) for a representative subset of
the simulation conditions. A negative difference indicates superior performance
of \ainet{}. In the second row, the arrows depict the change in the
pre-registered results after changing the data-generating process (E2). The
third row shows the result after removal of the elastic net competitor (E3).
Finally, the bottom row shows the end result where selective reporting of
simulation conditions and competitor methods (R2) is applied to give a more
favorable impression of \ainet{}. We will now discuss these QRPs in more detail.

\paragraph{Altering the data-generating process (E2)}
We could not detect a systematic performance benefit of \ainet{} over standard
logistic regression, elastic net regression, or random forest for the scenarios
specified in the protocol. For this reason, we tweaked the data-generating
process by adding different sparsity conditions and a non-linear effect. We then
found that \ainet{} outperforms logistic regression under the following
conditions: Only few variables being associated with the outcome (sparsity), a
non-linear effect and a low number of events per variable (EPV).
Figure~\ref{fig6:E1} (second row) shows the changes in Brier score difference
between the pre-registered and the tweaked simulation. As can be seen, the
tweaked data-generating process leads to \ainet{} being superior to competitors
in some conditions, and at least not inferior in others.

\paragraph{Removing competitor methods (E3)}
Despite the adapted data-generating process, we still observed only minor (if
any) improvements of \ainet{} over the elastic net. In order to present \ainet{}
in a better light we could omit the comparisons with the elastic net (E3), as
shown in Figure~\ref{fig6:E1} (third row). This could be justified, for example,
by arguing that for neutral comparison it is sufficient to compare a less
flexible method (logistic regression, which has no tuning parameters and
captures linear effects), a more flexible method (random forest, which has
tuning parameters and captures nonlinear relationships), and a comparably
flexible method (adaptive elastic net, which has the same tuning parameters as
AINET, but differs in the way the penalization weights are chosen).

\paragraph{Selective reporting of simulation results (R2)}
After the removal of the competitor elastic net, there are still some simulation
conditions under which \ainet{} is not superior to the remaining competitors. To
make \ainet{} appear more favorable, we thus report only simulation conditions
with low EPV, as shown in Figure~\ref{fig6:E1} (fourth row). This could be
justified by the fact that journals require authors to be concise in their
reporting. Otherwise, further conditions with low EPV values could be simulated
to make the results seem more exhaustive. Focusing primarily on low EPV settings
could be justified in hindsight by framing \ainet{} as a method designed for
high-dimensional data (low sample size relative to the number of variables).

\section{Recommendations}
\label{sec6:recommendations}

The previous sections painted a rather negative picture of how
undisclosed changes in simulation design, analysis and reporting
may lead to overoptimistic conclusions. In the
following, we summarize what we consider to be practical recommendations for
improving the methodological quality of simulation studies; see
Table~\ref{table6:recommendations} for an overview. Our recommendations are
grouped with regards to which stakeholder they concern.

\begin{table}[!htb]
  \caption{Recommendations for improving quality of comparative simulation studies
    and preventing QRPs.}
  \label{table6:recommendations}
  \centering
	\begin{tabular}{p{.95\textwidth}}
		\toprule
    \textit{Researchers} \\
    \midrule
    \vspace{-1.5em}
    \begin{itemize}
    \setlength\itemsep{0pt}
    \setlength\itemindent{-12pt}
        \item[--] Write (and possibly pre-register) simulation protocols
    \item[--] Adopt good computational practices (code review, packaging, unit-tests)
    \item[--] Share code and data (possibly in intermediate/summary form to enable
    secondary analysis)
    \item[--] Report the process of the simulation study fully and transparently
    (for instance, time-stamped protocol amendments to disclose pilot studies
    and \emph{post hoc} modifications)
    \item[--] Perform simulation analysis in a blinded manner
    \item[--] Collaborate with other research groups (possibly familiar with ``competing'' methods)
    \item[--] Disclose multiplicity and uncertainty of results (for example, with sensitivity analyses)
    \item[--] Teach simulation study methodology in statistics (post)graduate courses
    \end{itemize}

@@

\section{Conclusions} \label{sec6:discussion}

@@

\section{Simulation protocol}
\label{app6:protocol}

@@

\subsection{Aims} \label{sec6:aims}

The aim of this simulation study is to systematically study the predictive
performance of \ainet{} for a binary prediction task. The simulation conditions
should resemble typical conditions found in the development of prediction models
in biomedical research. In particular we want to evaluate the performance of
\ainet{} conditional on
\begin{itemize}
  \item low- and high-dimensional covariates
  \item (un-)correlated covariates
  \item small and large sample sizes
  \item varying baseline prevalences
\end{itemize}
\ainet{} will be compared to other (penalized) binary regression models
from the literature, namely
\begin{itemize}
  \item Binary logistic regression: the simplest and most popular method for
        binary prediction
  \item Elastic net: a generalization of LASSO and ridge regression, the most
        widely used penalized regression methods
  \item Adaptive elastic net: a generalization of the most popular weighted
  penalized regression method (adaptive LASSO)
  \item Random forest: a popular, more flexible method. This method is related to
        \ainet{}, see Section~\ref{sec6:methods}.
\end{itemize}
These cover a wide range of established methods with varying flexibility and
serve as a reasonable benchmark for \ainet. There are many more extensions of
the adaptive elastic net in the literature \citep[see \eg{} the review
by][]{Vidaurre2013}. However, most of these extensions focus on variable
selection and estimation instead of prediction, which is why we restrict our
focus only on the four methods above.

\subsection{Data-generating process} \label{sec6:dgp}

@@

\subsection*{Test data}
In order to test the out-of-sample predictive performance, we generate a test
data set of \mbox{$n_{\text{test}} = 10000$} data points in each simulation $b$.

\subsection{Estimands} \label{sec6:estimands}

@@

\subsection{Methods} \label{sec6:methods}

@@

\subsection{Performance measures} \label{sec6:performance}

The distribution of all estimands from Section~\ref{sec6:estimands} will be
assessed visually with box- and violin-plots that are stratified by method and
simulation conditions. We will also compute mean, median, standard deviation,
interquartile range, and 95\% confidence intervals for each of the estimands.
Moreover, instead of ``eye-balling'' differences in predictive performance
across methods and conditions, we will formally assess them by regressing the
estimands on the method and simulation conditions \citep[see][]{Skrondal2000}.
To do so, we will use a fully interacted model with the interaction between the
methods and the 128 simulations conditions, \ie in R notation: \texttt{estimand
  $\sim$ 0 + method:scenario}. We will rank pairwise comparison between two
methods within a single condition by their $p$-values, to more easily identify
conditions where methods show differences in predictive performance. The choice
of a significance level at which a method is deemed superior will be determined
based on preliminary simulations. We set this level to 5\%, where $p$-values
will be adjusted using the single-step method \citep{Hothorn2008} within a
single simulation condition for comparisons between \ainet{} and any other
method.

@@

\subsection{Handling exceptions} \label{sec6:exceptions}

@@

Figure~\ref{fig6:tiebrier} shows the differences in mean Brier score between
\ainet{} and the other methods stratified by simulation conditions. We see that
there is hardly any difference between \ainet{} and the elastic net (EN) across
all simulation conditions meaning that predictive performance of both methods
seems to be very similar in the investigated scenarios.

@@

Figure~\ref{fig6:tiesbrier} shows the differences in scaled Brier score between
\ainet{} and the other methods stratified by simulation conditions. The scaled
Brier score is useful to compare the actual values of Brier scores across
conditions with different prevalence, but not so much to compare Brier scores of
different methods within a simulation condition with fixed prevalence.

We see that for most conditions the plots look like a flipped version of the
original Brier scores from Figure~\ref{fig6:tiebrier}. Therefore, conclusions are
mostly the same. For very small sample sizes coupled with low prevalence and low
events per variable (the topleft plots), the scaled Brier score indicates
superiority of \ainet{} over RF and GLM, which is opposite the conclusion based
on the raw Brier score. We advise to interpret these conditions cautiously since
the prevalence prediction which is used for scaling is based on the much larger
test data set.

@@

Figure~\ref{fig6:tienll} shows the differences in log-score between \ainet{} and
the other methods stratified by simulation conditions. We see that in certain
conditions, the error bars of certain methods are much larger. This is due to
the log-score's sensitivity to extreme predictions, which often happen under the
RF (and sometimes under the GLM). Despite the larger variability of the
log-score, conclusion regarding the comparison between \ainet{} and the other
methods are largely the same as under the Brier score.

@@

Figure~\ref{fig6:tienll} shows the differences in area under the curve (AUC)
between \ainet{} and the other methods stratified by simulation conditions. As
with the other estimands, \ainet{} shows virtually identical performance as EN
regression across all simulation conditions. \ainet{} seems to outperform RF
across most simulation conditions, with the exception of a conditions with low
sample size ($n = 100$), medium prevalence ($\mbox{prev} = 0.05$), and low
events per variable ($\mbox{EPV} \leq 1$). GLM, typically outperforms \ainet{}
conditions with small to medium sample size ($n \leq 500$), and also in
conditions with larger sample size when the events per variable is normal to
high ($\mbox{EPV} \geq 10$) and the prevalence is small ($\mbox{prev} = 0.01$).
Finally, the AEN is worse with respect to AUC than \ainet{} across all
simulation conditions.

@@

Figure~\ref{fig6:cslope} shows boxplots of calibration slopes stratified by
simulation condition and method. For each condition the percentage of
simulations where no estimate could be obtained is indicated. This usually
happened because of extreme (close to zero or one) predictions, or
non-convergence of the method itself. We caution against interpretation of the
random forest (RF) calibration slopes because this method often resulted in
predicted probabilities of zero or one, so that a calibration slope could not be
fitted.

@@

Figure~\ref{fig6:clarge} shows boxplots of calibration in the large estimates
stratified by simulation condition and method. For each condition also the
percentage of simulations where no estimate could be obtained is indicated. This
usually happened because of extreme (close to zero or one) predictions.

@@

\begin{landscape}
\begin{figure}[!ht]
\center
\includegraphics[width=0.9\linewidth]{images/paper6/tie-fighter_brier_sparsity0.pdf}
\caption{Tie-fighter plot for the difference in Brier score between any method
  on the $y$-axis and \ainet{}. The 95\% confidence intervals are adjusted per
  simulation condition using the single-step method. Lower values indicate
  better performance of \ainet{}. } \label{fig6:tiebrier}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}[!ht]
\center
\includegraphics[width=0.9\linewidth]{images/paper6/tie-fighter_scaledBrier_sparsity0.pdf}
\caption{Tie-fighter plot for the difference in scaled Brier score between any
  method on the $y$-axis and \ainet{}. The 95\% confidence intervals are adjusted
  per simulation condition using the single-step method. Larger
  values indicate better performance of \ainet{}. } \label{fig6:tiesbrier}
\end{figure}
\end{landscape}
